---
title: "Convert Outline to R Notebook/Bookdown Recipe"
date: "`r Sys.Date()`"
output: html_document
---

## Make R Notebook/Bookdown from Text Outline {#outline-to-r-doc}

## Ingredients

* Text outline
* Output format choice (notebook/bookdown)
* Chapter/section organization
* Code needs
* Output requirements
* Cross-reference needs

## Instructions

Use this prompt template:

````
Please convert this outline to [a R notebook/R bookdown site]:

```
[paste outline here]
```

### Structure needs:
* Format: [notebook/bookdown]
* Organization:
    - [single/multiple files]
    - [chapter structure]
    - [section depth]
* Special features:
    - [cross-references]
    - [bibliography]
    - [numbering]
    - [table of contents]

### Code requirements:
* Code chunks: [yes/no]
* Languages: [R/Python/etc]
* Output: [tables/plots/etc]
* Chunk options: [specific needs]

### Additional elements:
* Theme: [if specific needed]
* Citations: [if needed]
* Custom formatting: [special needs]
* Navigation: [requirements]
````

## Tips

* Maintain hierarchy
* Consider depth
* Plan navigation
* Think about code
* Include examples
* Note dependencies
* Consider format
* Check structure

## Serves

* Course materials
* Documentation
* Research reports
* Technical books
* Analysis reports
* Tutorials
* Guides

## Example

````
Please convert this outline to an R bookdown site:

```
Data Analysis with R
1. Introduction
   - About this book
   - Prerequisites
   - Setup
2. Data Import
   - CSV files
   - Excel files
   - Database connections
3. Data Cleaning
   - Missing values
   - Outliers
   - Data types
4. Analysis
   - Summary statistics
   - Visualization
   - Models
```

### Structure needs:
* Format: bookdown site
* Organization:
    - Separate file per chapter
    - Two heading levels
    - Numbered sections
    - Chapter navigation
* Special features:
    - Code folding
    - Figure/table numbers
    - Cross-references
    - Search function

### Code requirements:
* Code chunks: yes
* Languages: R
* Output: plots, tables
* Chunk options:
    - Echo code
    - Show results
    - Allow folding

### Additional elements:
* Theme: default
* Citations: none needed
* Custom formatting: none
* Navigation: chapter menu
````

## Common Structures

### 1. File Organization

1. **R Notebook**
```yaml
---
title: "Project Title"
output: html_notebook
---

# Main heading

## Sub heading

### Sub-sub heading
```

2. **Bookdown Project**
```
project/
├── index.Rmd
├── 01-intro.Rmd
├── 02-chapter2.Rmd
├── _bookdown.yml
├── _output.yml
└── style.css
```

### 2. Configuration Files

1. **_bookdown.yml**
```yaml
book_filename: "book"
language:
  ui:
    chapter_name: "Chapter "
delete_merged_file: true
output_dir: "docs"
```

2. **_output.yml**
```yaml
bookdown::gitbook:
  css: style.css
  config:
    toc:
      collapse: subsection
      scroll_highlight: yes
    download: ["pdf", "epub"]
```

### 3. Content Elements

1. **Code Chunks**
````markdown
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r chunk-name}
# R code here
```
````

2. **Cross-References**
```markdown
# Chapter Title {#chapter-label}

See Chapter \@ref(chapter-label)

See Figure \@ref(fig:plot-label)
```

### 4. Special Features

1. **Parts Organization**
```markdown
# (PART) Part Title {-}

# First Chapter in Part
```

2. **Custom Blocks**
```markdown
::: {.note}
Note content here
:::

::: {.warning}
Warning content here
:::
```

3. **Math/Equations**
```markdown
Inline math: $y = mx + b$

Display math:
$$
y = \beta_0 + \beta_1x + \epsilon
$$
```

